Tabular Constraint Learning

### 2016-04-15 Paper/ECAI/tabular.tex
lines

    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\discrete(v_x)$ & All values in $v_x$ are different: $v_x[i] \neq v_x[j]$ if $i \neq j$ \\

@@

@@

    \ecfkey{v_{fk}}{v_{pk}} & $v_{fk}$ and~$v_{pk}$ are both $\discrete$; $\ptype(v_{fk}) = \ptype(v_{pk})$; $\ptable(v_{fk}) \neq \ptable(v_{pk})$; and $\ecalldiff{v_{pk}}$ & Every value in~$v_{fk}$ also exist in~$v_{pk}$ \\

>>>>

    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\ \hline \hline
    \ecalldiff{v_x}
      & $\discrete(v_x)$
      & All values in $v_x$ are different: $v_x[i] \neq v_x[j]$ if $i \neq j$
      \\ \hline

@@

      \\ \hline

@@

      \\ \hline
    \ecfkey{v_{fk}}{v_{pk}} & $v_{fk}$ and~$v_{pk}$ are both $\discrete$; $\ptype(v_{fk}) = \ptype(v_{pk})$; $\ptable(v_{fk}) \neq \ptable(v_{pk})$; and $\ecalldiff{v_{pk}}$ & Every value in~$v_{fk}$ also exist in~$v_{pk}$ \\ \hline
